The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)

### 2018-10-14 outputs/docs/events/paper.Rmd
Fix annoying minor typos

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Effect of Events on Australian Federal Parliamentary Discussion (1901--2017)"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, Chris Cochrane and Dan Simpson for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources. Comments on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We systematically analyse how parliamentary discussion changes in response to different types of events in Australian history. We first create a dataset of what was said in the Australian Federal parliament from 1901 through to 2017 based on available public records. To reduce the dimensionality of this dataset we use a correlated topic model. We analyse the effect of various events using a Bayesian hierarchical Dirichlet model. We find that: 1) changes in government tend be associated with topic changes even when the party in power does not change; 1) elections that do not result in a change in government are rarely associated with topic changes; 2)  3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks. Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media and political cycle becomes increasingly focused on short-term events."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

In this paper we examine text records of what was said in Australian's federal parliament. We create a dataset based on all sitting days from 1901 through to 2017. Over this period we have records for 7,869 days in the House of Representatives and 6,682 days in the Senate, although we drop a handful of days for various reasons. Our dataset consists of counts of every word that occurs at least thrice, after we convert all words to lowercase, remove punctuation and numbers and join commonly collocated words.

@@

The advantage of using an analysis model in this way is that it: allows the events to have more-complicated autocorrelated functional forms; allows us to implement pooling across groups of similar documents; and it identifies outlying topic distributions without the need to pre-specify the event of interest. The main weakness of this approach is that it does not appropriately propagate uncertainty and future models should improve on this.

We find: 1) changes in government tend be associated with topic changes even when the party in power does not change. For instance, the change from Menzies to Holt in 1966; the change from Hawke to Keating in 1991; and the change from Rudd to Gillard in 2010 are all associated with significant changes in topics despite no change in the party in power. 2) As expected, elections where the party in power also changes, such as Whitlam in 1972, Hawke in 1983, Howard in 1996, Rudd in 2007, and Abbott in 2013 are associated with topic changes, but the 2001 and 2004 Howard re-elections stand out as elections where the government was returned yet there was a significant change in topics. 3) Economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks. **[More here on that one.]** **[Do we have different slopes that we could talk about?]**

Our work contributes to a growing modern quantitative social sciences literature that considers text as an input to more traditional methods, rather than requiring separate analysis. As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in this approach to only increase.

@@

# Data
## Parliamentary text data
Following the example of the UK a daily text record called Hansard of what was said in Australian parliaments has been made available since their establishment.[^Verbatimfootnote] Earlier work on the influence of parliaments, such as @ZandenBuringhBosker2012, often examined broader activity measures such as counts of sitting days. This allowed for long time-frames and wide comparisons. But analysing Hansard records and their equivalents directly is increasingly viable as new methods and reduced computational costs make it easier.

@@

Australian parliaments generally make their daily Hansard records available online as PDFs and these are considered the official release. Additionally, XML records are available in some cases.[^XMLfootnote] We detail the sources of our Hansard PDFs in \@ref(hansardsources) and Appendix \@ref(examplehansardpage) provides an example of what a Hansard PDF looks like. There are 14,551 days worth of publicly available Hansard records across the houses of federal parliament. Our data cleaning process indicates concerns with a small number of PDFs and these are detailed in Appendix \@ref(knownhansardissues).

@@

# Results
We are interested in considering the effect of various events on what is talked about in Australia's parliaments. 
<!-- Each of the parliaments and their houses are treated independently here. Future work could expand the model to better understand, and allow, for correlation between them.  -->
Political events are those related to a change of government or an election. Other events are defined by substantial changes in various economic measures, such as the onset of the Great Depression or floating the currency; events of a historical magnitude, such as entering into a war or the 9/11 attacks; or events that had a significant effect on Australian life, such as hosting the Olympics, or the Mabo decision. The full list of events that we consider are detailed in Appendix \@ref(eventdetails).

@@

>>>>

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, Chris Cochrane and Dan Simpson for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources. Comments on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We systematically analyse how parliamentary discussion changes in response to different types of events in Australian history. We first create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2017 based on available public records. To reduce the dimensionality of this dataset we use a correlated topic model. We analyse the effect of various events using a Bayesian hierarchical Dirichlet model. We find that: 1) changes in government tend be associated with topic changes even when the party in power does not change; 2) elections that do not result in a change in government are rarely associated with topic changes; 3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks. Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media and political cycle becomes increasingly focused on short-term events."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

In this paper we examine text records of what was said in the Australian Federal Parliament. We create a dataset based on all sitting days from 1901 through to 2017. This means that we have records for 7,869 days in the House of Representatives and 6,682 days in the Senate, although we drop a handful of days for various reasons. Our dataset consists of counts of every word that occurs at least thrice, after we convert all words to lowercase, remove numbers and punctuation, join commonly co-located words, and remove stop words.

@@

We find: 1) changes in government tend be associated with topic changes even when the party in power does not change. For instance, the change from Hughes to Bruce in 1922, Menzies to Holt in 1966; Hawke to Keating in 1991; and Rudd to Gillard in 2010 are all associated with significant changes in topics despite no change in the party in power. 2) As expected, elections where the party in power also changes, such as Whitlam in 1972, Hawke in 1983, Howard in 1996, Rudd in 2007, and Abbott in 2013 are associated with topic changes, but the 2001 and 2004 Howard re-elections stand out as elections where the government was returned yet there was a significant change in topics. 3) Economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks. **[More here on that one.]** **[Do we have different slopes that we could talk about?]**

Our work contributes to a growing modern quantitative social sciences literature that considers text as an input to more traditional methods, rather than requiring separate analysis. The advantage of using our analysis model is that it: allows the events to have more-complicated autocorrelated functional forms; allows us to implement pooling across groups of similar documents; and it identifies outlying topic distributions without the need to pre-specify the event of interest. The main weakness of this approach is that it does not appropriately propagate uncertainty and future models should improve on this. As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in this approach to only increase.

@@

# Data
## Parliamentary text data
Following the example of the UK a daily text record called Hansard of what was said in the Australian Federal Parliament has been made available since it was established in 1901.[^Verbatimfootnote] Earlier work on the influence of parliaments, such as @ZandenBuringhBosker2012, often examined broader activity measures such as counts of sitting days. This allowed for long time-frames and wide comparisons. But analysing Hansard records and their equivalents directly is increasingly viable as new methods and reduced computational costs make it easier.

@@

The Australian Federal Parliament makes daily Hansard records available online as PDFs and these are considered the official release. Additionally, XML records are available in some cases.[^XMLfootnote] We detail the sources of our Hansard PDFs in \@ref(hansardsources) and Appendix \@ref(examplehansardpage) provides an example of what a Hansard PDF looks like. There are 14,551 days worth of publicly available Hansard records across both chambers of the Australian Federal Parliament. Our data cleaning process indicates concerns with a small number of PDFs and these are detailed in Appendix \@ref(knownhansardissues).

@@

# Results
We are interested in considering the effect of various events on what is talked about in the Australian Federal Parliament.
<!-- Each of the parliaments and their houses are treated independently here. Future work could expand the model to better understand, and allow, for correlation between them.  -->
Political events are those related to a change of government or an election. Other events are defined by substantial changes in various economic measures, such as the onset of the Great Depression or floating the currency; events of a historical magnitude, such as entering into a war or the 9/11 attacks; or events that had a significant effect on Australian life, such as hosting the Olympics, or the Mabo decision. The full list of events that we consider are detailed in Appendix \@ref(eventdetails).

@@

Add discussions about weakenss of the model.

Add other discussion that I thought of and now forget.
